\begin{abstract}
    % \section*{Abstract}
    \addcontentsline{toc}{section}{Abstract}
    \begin{center}
        \vspace*{1cm}

        \huge
        % \textbf{HKUST (GZ)}
        \vspace{0.5cm}
        
        \textbf{RBM Research Proposal}

        \vspace{3cm}

    \end{center}
    
    \textbf{Abstract: }
    % \textit{Thesis Proposal for Red Bird Mphil}. 
    In the rapidly evolving landscape of technology, the integration of Artificial Intelligence into content generate within the metaverse has become a focal point. 
    However, the current technological faces challenges in optimizing multi-AI agent and multi-player interactions for narrative enrichment.
    This study explores the intersection of Artificial Intelligence and narrative gaming within the metaverse, conducting a comparative analysis of existing multi-AI agent and multi-player interaction models. 
    We dissects their strengths and weaknesses to propose refinements with a focus on enhancing multi-player interactions and storytelling. 
    The methodological approach involves the development and testing of a specialized AI-Player interactive collaborative decision-making system 
    tailored for narrative metaverse games, with an emphasis on exploring realistic and effective methods for AI-Player interaction and decision-making 
    to elevate game immersion and user experiences in narrative contexts. 
    In the team project, this research provides a comprehensive theoretical framework 
    for addressing the complexities of multi-AI agent and multi-player interactions. 
    Comparative research and experimental findings contribute suggestions and solutions 
    to enhance the AI-Player interactive experience, aligning with the overarching goal of the team project. 
    Furthermore, the development of a collaborative decision-making system for multi-AI agents and multi-player interactions 
    is poised to elevate interactivity and advance the broader scope of AI-driven metaverse games.

    % \setcounter{page}{2} % set the page number to 2
\end{abstract}