

\section*{Part \uppercase\expandafter{\romannumeral2} Proposal of the Individual Project}
\addcontentsline{toc}{section}{Part \uppercase\expandafter{\romannumeral2} Proposal of the Individual Project} 
\setcounter{section}{2}
\setcounter{subsection}{0}

%  -----  2.1
\subsection{Significance and Relevance of the Individual Project to the Group Project}
Briefly describe the group project.

\subsubsection{Complementary Role}
Explain how your project complements the broader objectives of the group project. 
Discuss how your work fills a necessary gap or adds a unique perspective to the collective effort.

\subsubsection{Value Addition}
Describe the specific ways in which your project adds value to the group project. 
This might include the development of critical components, providing specialized knowledge or skills, or enhancing the overall quality and scope of the group project.

\subsubsection{Interdependence}
Highlight any dependencies between your project and other components of the group project. 
Explain how collaboration and coordination with other group members are integral to achieving both individual and group objectives.


%  -----  2.2
\subsection{Statement of the Individual Project in Details}
Briefly describe the group project.

\subsubsection{Literature/Market Review and Problem Definition}

\subsubsection{Objective and Scope of the Project}

\subsubsection{Research Method and Justification}

\subsubsection{Execution Plan}

\subsubsection{Intended Outcomes}

Outcome 1: Description \& relation of this outcome to the group project. 

Outcome 2: Description \& relation of this outcome to the group project. 

Outcome 3: Description \& relation of this outcome to the group project.


%  -----  2.3
\subsection{Project Milestones}
Table the group project and the individual project milestones. 
Illustrate the relation and alignment of milestones of the individual project and those of the group project.


%  -----  2.4
\subsection{Budget Plan}
Briefly describe the group project.

\subsubsection{Budget Breakdown}
Break down the budget into categories.

\subsubsection{Cost-Effectiveness}
Discuss cost-effectiveness.


%  -----  2.5
\subsection{Risk Analysis and Mitigation}
Briefly describe the group project.

\subsubsection{Potential Risks or Challenges}
Identify potential risks or challenges that may arise during implementation of the project.

\subsubsection{Impact of the Risks}
Assess the impact of the risks to the success of the project and propose mitigation strategies.